Age-structured transmission dynamic models of RSV

### 2023-01-24 1_MSIS_model_explain/MSIS_model_explain.Rmd
update example

## References

@@

## Section outlines
\
- In the first section, we will learn how to run transmission model with all parameters known. 
\
\
- In the second section, we will learn to use maximum a posteriori / maximum likelihood estimation (MLE) to estimate the unknown parameters (one value for each unknown parameter). 
\
\
- In the third section, we will learn to use STAN, a probabilistic programming language for statistical inference^[https://en.wikipedia.org/wiki/Stan_(software)], to get the 95% credible intervals from the posterior samples of these unknown parameters.

## Section 1: run transmission model with all parameters known
\
We first assign values to all required parameters, including rates and probabilities. Most of these are described in Table 2 of Pitzer et al, PLOS Pathogens^[https://journals.plos.org/plospathogens/article?id=10.1371/journal.ppat.1004591]
\
\
```{r, echo=T}
###########################################
# omega = 1/duration of maternal immunity 
DurationMatImmunityDays= 30 #days
###########################################

@@

## Section 2: use maximum a posteriori (variation of MLE) to estimate the unknown parameters

@@

## Section 3: Stan model to estimate posterior samples

>>>>

## Section outlines
\
- In the first section, we introduces the background knowledge of transmission dynamic models of RSV.
\
\
- In the second section, we will learn how to run transmission model with all parameters known. 
\
\
- In the third section, we will learn to use maximum a posteriori / maximum likelihood estimation (MLE) to estimate the unknown parameters (one value for each unknown parameter). 
\
\
- In the fourth section, we will learn to use STAN, a probabilistic programming language for statistical inference^[https://en.wikipedia.org/wiki/Stan_(software)], to get the 95% credible intervals from the posterior samples of these unknown parameters.

## Section 1: prerequisite readings (references)

@@

## Section 2: run transmission model with all parameters known
\
We first assign values to all required parameters, including rates and probabilities. Most of these are described in Table 2 of Pitzer et al, PLOS Pathogens^[https://journals.plos.org/plospathogens/article?id=10.1371/journal.ppat.1004591]
\
\
```{r, echo=T}
###########################################
# omega = 1/duration of maternal immunity 
DurationMatImmunityDays= 30 #days
###########################################

@@

## Section 3: use maximum a posteriori (variation of MLE) to estimate the unknown parameters

@@

## Section 4: Stan model to estimate posterior samples
